### 2011-01-26 paper/platformDetails.tex

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.

@@

>>>>

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.
\acmFig{quadratot.jpg}{1}{The robot}
\acmFig{topdown.png}{1}{A figure of the robot from a top-down perspective,
with motors labeled}

@@

\acmFig{robot.JPG}{1}{The infrared LED mounted on top of the robot, which
provides feedback about distance traveled in conjunction with a Wii
remote}
\acmFig{wiiMote.JPG}{1}{A Wii remote tracks the location of the robot,
providing feedback about distance traveled}
